|

### 2024-11-23 paper/manuscript.Rmd
initial revisions for the R&R.

Why is this important? After all, if we can produce reasonable estimates at the population level, this must surely be enough. We believe that there are at least two reasons why we should care about this problem. First, the inability to identify the individuals who truly change gives us a false sense of homogeneity. When we report an average change of, say, 0.10 standard deviations, we do not know whether this reflects uniform change across all individuals, or significant changes in some while others remain stable. This is a big substantive difference, yet often overlooked in practice. Second, if we do not know the changers in the first place, our comparisons between groups---either across some pre-determined characteristic, or across treatment status---will average true processes with false negatives and false positives. This is obviously fine if the error occurs randomly, but it is challenging to verify this if individual-level accuracy is compromised. Hence, glossing over this problem discourages us to think about what exactly we are averaging.

@@

We can now clearly state our research question: given a longitudinal panel study where we observe some individuals across time, how can we determine the underlying generative process---that is, how many people changed, how much they changed, and who changed---given a level of latent score reliability, response resolution, and a longitudinal survey design?

>>>>

Why is this important? After all, if we can produce reasonable estimates at the population level, this must surely be enough. We believe that there are at least two reasons why we should care about this problem. First, the inability to identify the individuals who truly change gives us a false sense of homogeneity. When we report an average change of, say, 0.10 standard deviations, we do not know whether this reflects uniform change in latent positions across all individuals, or significant changes in some while others remain stable. This is a big substantive difference, yet often overlooked in practice. Second, if we cannot identify the "changers" in the first place, our comparisons between groups---either across some pre-determined characteristic, or across treatment status---will average true processes with false negatives and false positives. This is obviously fine if the error occurs randomly, but it is challenging to verify this if individual-level accuracy is compromised. Hence, glossing over this problem discourages us to think about what exactly we are averaging.

@@

We can now clearly state our research question: given a longitudinal panel study where we observe some individuals across time, how can we determine the underlying generative process---that is, how many people changed, how much their latent positions changed, and who changed---given a level of latent score reliability, response resolution, and a longitudinal survey design?
